Rusty Variation

### 2018-06-14 doc/main.tex
Wrote deadlocking examples into the library; refined draft

\documentclass[sigconf,UKEnglish,natbib=false]{acmart}
\input{preamble}

@@

The \lstinline{new} function generates a new session and returns two \emph{dual} channel endpoints. Unlike the rest of the functions discussed in this section, \lstinline{new} is \emph{not} part of the public interface.

@@

While these functions suffice to encode choice, we also define two macros, \lstinline{offer!} and \lstinline{select!}, which generalise this functionality to \emph{all enums}---as long as each value wraps a session. This allows processes to offer and select choices between many \emph{labelled} branches, and allows us to define the type for our calculator server as:
\begin{lstlisting}
type CalcSrv = Recv<CalcOp, End>;
enum CalcOp {Neg(NegSrv), Add(AddSrv)}
\end{lstlisting}
Using these macros, we can write the following program. This program forks off a calculator server, which offers the choice between negation and addition, selects addition, sends some numbers, and then returns the result:
\begin{lstlisting}
let s = fork!(move |s: CalcSrv| {
  offer!(s, {
    CalcOp::Neg(s) => {
      let (x, s) = recv(s)?;
      send(-x, s)
    },
    CalcOp::Add(s) => {
      let (x, s) = recv(s)?;
      let (y, s) = recv(s)?;
      send(x + y, s)
    },
  })
});
let s = select!(CalcOp::Add, s)?;
let s = send(4, s)?;
let s = send(5, s)?;
let (z, End) = recv(s)?;
Ok(z)
\end{lstlisting}

\subsection*{Limitations}
There are two issues which can make code written using Rusty Variation deadlock, and surprisingly, \lstinline{unsafe} is not one of them:

@@

Last, the implementation Rusty Variation is inefficient. We currently use the asynchronous channels from \lstinline{std::sync::mpsc}. These are ideal, as they already implement the correct cancellation behaviour. Unfortunately, they can send values of only a single type. Therefore, in the implementation of \lstinline{send}, we create a new session for the continuation, and send that along with the value. This means we create a ``one-shot'' channel for every call to \lstinline{send}.

>>>>

\documentclass[sigconf,natbib=false]{acmart}
\input{preamble}

@@

The \lstinline{new} function generates a new session and returns two \emph{dual} channel endpoints. Unlike the rest of the functions discussed in this section, \lstinline{new} is \emph{not} part of the public interface---see \cref{sec:limitations}.

@@

While these functions suffice to encode choice, we also define two macros, \lstinline{offer!} and \lstinline{select!}, which generalise this functionality to \emph{all enums}---as long as each value wraps a session. This allows processes to offer and select choices between many \emph{labelled} branches, and allows us to define the type for our calculator server as:
\begin{lstlisting}
type CalcSrv = Recv<CalcOp, End>;
enum CalcOp {Neg(NegSrv), Add(AddSrv)}
\end{lstlisting}
Using these macros, we can write the following program. This program forks off a calculator server, which offers the choice between negation and addition, selects addition, sends some numbers, and then returns the result:
\begin{lstlisting}
let s = fork!(move |s: CalcSrv| { offer!(s, {
    CalcOp::Neg(s) => {
      let (x, s) = recv(s)?;
      send(-x, s)
    },
    CalcOp::Add(s) => {
      let (x, s) = recv(s)?;
      let (y, s) = recv(s)?;
      send(x + y, s)
    },})});
let s = select!(CalcOp::Add, s)?;
let s = send(4, s)?;
let s = send(5, s)?;
let (z, End) = recv(s)?;
Ok(z)
\end{lstlisting}

\subsection*{Implementation}
We use the asynchronous channels from \lstinline{std::sync::mpsc}. These are ideal, as they already implement the correct cancellation behaviour. However, they can only transfer values of a single type. Therefore, we treat them as linear channels---channels which can only be used once---and encode our communication following \textcite{dardha2017}. Each \lstinline{send} creates a new channel for the continuation of the session, and sends that along with the value. Fortunately, the channels in \lstinline{std::sync::mpsc} are highly optimised for one-shot usage.

\subsection*{What If I Want to Be Evil?}\label{sec:limitations}
There are three ways in which you can make code written using Rusty Variation deadlock. The first is by looping, which we discussed earlier. The other two are both explicit, and surprisingly, \lstinline{unsafe} is not one of them:

@@
